Apparent preferences for cognitive effort fade when multiple forms of effort

### 2020-12-07 Cost_manuscript.Rmd
stats for the btw subj fits added

## BIC
# keep relevant model results and combine into a single df with generalizable names (delete eventually)
temp_btw <- fits_bic_btw[c(1, 3, 4, 6), ]
temp_wth <- fits_bic_wth[c(1, 3, 13, 15), ]
temp_btw$wth <- temp_wth$bic
colnames(temp_btw) <- c("Model", "Between", "Within")
modelComparison <- temp_btw %>% gather(Exp, BIC, -Model)
rm(temp_btw, temp_wth, fits_bic_btw, fits_bic_wth)

@@

## Model fit summaries
# mean and sd of parameters from winning model (exp some? still confused)
# parameter order for wth: gamma, alpha, C, w_decay, beta
mFits_btw <- sapply(fits_btw$`Adaptive OC + Biased OC`, function(group) {apply(group$x, 1, mean)})
sdFits_btw <- sapply(fits_btw$`Adaptive OC + Biased OC`, function(group) {apply(group$x, 1, sd)})

@@

## Compare
# BTW
# first, divide the group fits into a list of dataframes for each parameter
t <- lapply(fits_btw$`Adaptive OC + Biased OC`, function(group) {melt(group$x, value.name = "Fit")})
n <- names(fits_btw$`Adaptive OC + Biased OC`)
reshaped <- mapply(cbind, t, "Group" = n, SIMPLIFY = F)
aovShape_btw <- do.call(rbind, reshaped) %>% 
                  filter(Group != "pheasy") %>%
                  plyr::dlply("Var1", identity)
rm(t, n)

@@

# and effect sizes
fitES <- aovShape_btw$cost %>%
  select(Group, Fit) %>%
  plyr::dlply("Group", identity) %>%
  do.call(cbind, .) %>%
  select_if(is.numeric) %>%
  rename(Physical = phys.Fit,
         Cognitive = cogTask.Fit,
         Wait = wait.Fit) %>%
  outer(., ., FUN = Vectorize(DescTools::CohenD))

## plot
# BTW
# select a parameter to plot
param <- do.call(rbind, aovShape_btw)
paramPlot <- ggplot(param, aes(Group, Fit, fill = Group)) +
    # geom_hline(yintercept = 0.64, alpha = 0.9, color = "gray20", size = 1) +
    # geom_hline(yintercept = 0.7, alpha = 0.9, color = "gray40", size = 1) +
    # geom_hline(yintercept = 0.9, alpha = 0.9, color = "gray60", size = 1) +
    #geom_hline(yintercept = 0, alpha = 0.9, size = 1, linetype = "dashed") + # mean of highest earning rates across blocks
    #geom_dotplot(stackdir = 'center', binaxis = 'y', show.legend = F) +
    geom_boxplot(show.legend = F) +
    geom_jitter(width = 0.1, alpha = 0.5, show.legend = F, pch = 21, size = 3) +
    #ylim(0,1.5) +
    labs(x = "") +
    facet_wrap(vars(Var1), scales = "free") +
    scale_fill_manual(values = colsBtw) +
    theme(panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.background = element_blank(),
          axis.line = element_line(colour = "black"),
          text = element_text(size = 16))

# WTH

@@

  The fourth model produced the lowest BIC in both experiments (Figure 10A. Between-subjects = $modelComparison[4, 3]$; Within-subjects = $modelComparison[8, 3]$). Figure 10B shows the parameter fits from the between-subjects experiment. Among these, the learning rate of the opportunity cost ($\alpha$) and the bias imposed by each demand on its estimate ($C_{demand}$) were of particular interest. Analyses of variance showed significant differences only for $c_{demand}$ (F(`r aovBtw$cost[[1]]$Df[1]`, `r aovBtw$cost[[1]]$Df[1]`) = `r fitFvals["cost"]`, *p* `r report_p(fitPvals["cost"])`), with $\alpha$ being uniformly low for all groups. Pairwise post-hoc permutations confirmed that the cognitive group () had lower biases than either wait () or physical () groups. Furthermore, these estimates were significantly lower than zero (tstats). These fits suggest that individuals integrated the opportunity cost of time at similar rates regardless of the concomitant demand, but that cognitive tasks boost the value of offers (**reword**).

  The fits of the model provided good qulitative resemblance to the observed choice behavior in both experiments (*Figure 10X*)

>>>>

### BIC
# keep relevant model results and combine into a single df with generalizable names (delete eventually)
temp_btw <- fits_bic_btw[c(1, 3, 4, 6), ]
temp_wth <- fits_bic_wth[c(1, 3, 13, 15), ]
temp_btw$wth <- temp_wth$bic
colnames(temp_btw) <- c("Model", "Between", "Within")
modelComparison <- temp_btw %>% gather(Exp, BIC, -Model)
rm(temp_btw, temp_wth, fits_bic_btw, fits_bic_wth)

@@

### Model fit summaries
# mean and sd of parameters from winning model (exp some? still confused)
# parameter order for wth: gamma, alpha, C, w_decay, beta
mFits_btw <- sapply(fits_btw$`Adaptive OC + Biased OC`, function(group) {apply(group$x, 1, mean)})
sdFits_btw <- sapply(fits_btw$`Adaptive OC + Biased OC`, function(group) {apply(group$x, 1, sd)})

@@

### Compare/analyze fits
## BTW
# first, divide the group fits into a list of dataframes for each parameter
t <- lapply(fits_btw$`Adaptive OC + Biased OC`, function(group) {melt(group$x, value.name = "Fit")})
n <- names(fits_btw$`Adaptive OC + Biased OC`)
reshaped <- mapply(cbind, t, "Group" = n, SIMPLIFY = F)
aovShape_btw <- do.call(rbind, reshaped) %>% 
                  filter(Group != "pheasy") %>%
                  plyr::dlply("Var1", identity)
rm(t, n)

@@

# effect sizes
fitES <- aovShape_btw$cost %>%
  select(Group, Fit) %>%
  plyr::dlply("Group", identity) %>%
  do.call(cbind, .) %>%
  select_if(is.numeric) %>%
  rename(Physical = phys.Fit,
         Cognitive = cogTask.Fit,
         Wait = wait.Fit) %>%
  outer(., ., FUN = Vectorize(DescTools::CohenD)) %>%
  abs() %>%
  round(digits = 2)

# and two-sided, one-sample t-test against 0
fitOStest <- aovShape_btw$cost %>%
  group_by(Group) %>%
  summarise(tresults = list(t.test(Fit, mu = 0)))

### plot parameter boxplots
## BTW
param <- do.call(rbind, aovShape_btw)
paramPlot <- ggplot(param, aes(Group, Fit, fill = Group)) +
    geom_boxplot(show.legend = F) +
    geom_jitter(width = 0.1, alpha = 0.5, show.legend = F, pch = 21, size = 3) +
    labs(x = "") +
    facet_wrap(vars(Var1), scales = "free") +
    scale_fill_manual(values = colsBtw) +
    theme(panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.background = element_blank(),
          axis.line = element_line(colour = "black"),
          text = element_text(size = 16))

## WTH

@@

  The fourth model produced the lowest BIC in both experiments (Figure 10A. Between-subjects = $modelComparison[4, 3]$; Within-subjects = $modelComparison[8, 3]$). Figure 10B shows the parameter fits from the between-subjects experiment. Among these, the learning rate of the opportunity cost ($\alpha$) and the bias imposed by each demand on its estimate ($C_{demand}$) were of particular interest. Analyses of variance showed significant differences only for $c_{demand}$ (F(`r aovBtw$cost[[1]]$Df[1]`, `r aovBtw$cost[[1]]$Df[1]`) = `r fitFvals["cost"]`, *p* `r report_p(fitPvals["cost"])`), with $\alpha$ being uniformly low for all groups. Pairwise post-hoc permutations confirmed that the cognitive group (mean = `r round(mFits_btw["cost", "cogTask"], digits = 2)`, SD = `r round(sdFits_btw["cost", "cogTask"], digits = 2)`) had lower biases than either wait (mean = `r round(mFits_btw["cost", "wait"], digits = 2)`, SD = `r round(sdFits_btw["cost", "wait"], digits = 2)`; *p* `r report_p(fitPerms["Cognitive", "Wait"])`; Cohen's D = `r fitES["Cognitive", "Wait"]`) or physical (mean = `r round(mFits_btw["cost", "phys"], digits = 2)`, SD = `r round(sdFits_btw["cost", "phys"], digits = 2)`; *p* `r report_p(fitPerms["Cognitive", "Physical"])`; Cohen's D = `r fitES["Cognitive", "Physical"]`) groups. These biases were significantly higher than zero for the wait group (t(`r fitOStest$tresults[[1]]$parameter`) = round(`r fitOStest$tresults[[1]]$statistic, digits = 2)`, *p* `r report_p(fitOStest$tresults[[1]]$p.value)`), and lower for the cognitive group (t(`r fitOStest$tresults[[2]]$parameter`) = round(`r fitOStest$tresults[[2]]$statistic, digits = 2)`, *p* `r report_p(fitOStest$tresults[[2]]$p.value)`). This suggests that rather than reducing costs, cognitive tasks boosted the value of their concommitant offers.

  **within**
  The fits of the model provided good qulitative resemblance to the observed choice behavior in both experiments (*Figure 10X*)
